COSC3500 \\ 2D Orbital Simulation Report

### 2018-10-18 reports/ms1_report.tex
Update report

This can be achieved with \texttt{MPI\_Scatterv} and \texttt{MPI\_Gatherv}
\footnote{These \texttt{v} variants support custom chunking sizes e.g. if we have 15 bodies we can send $4, 4, 4, 3$ bodies to each node respectively, which \texttt{MPI\_Scatter} and \texttt{MPI\_Gather} do not support dynamic chunking}. We decompose each dimension of our \texttt{Body}s into arrays, (e.g. the $x$ position, the $x$ veolocity, etc.), \texttt{MPI\_Scatterv} these arrays, recompose them into \texttt{Body}s, run \texttt{Leapfrog} on this subset on each node, decompose the subset into arrays, \texttt{MPI\_Gatherv} these arrays back to the root node, and recompose them into $\texttt{Bodys}$.

@@

\medskip

>>>>

This can be achieved with \texttt{MPI\_Scatterv} and \texttt{MPI\_Gatherv}
\footnote{These \texttt{v} variants support custom chunking sizes e.g. if we have 15 bodies we can send $4, 4, 4, 3$ bodies to each node respectively, which \texttt{MPI\_Scatter} and \texttt{MPI\_Gather} do not support dynamic chunking}. We decompose each dimension of our \texttt{Body}s into arrays, (e.g. the $x$ position, the $x$ veolocity, etc.), \texttt{MPI\_Scatterv} these arrays, recompose them into \texttt{Body}s, run \texttt{Leapfrog} on this subset on each node, decompose the subset into arrays, \texttt{MPI\_Gatherv} these arrays back to the root node, and recompose them into \texttt{Body}s.

@@

\section*{Testing}

\subsection*{Changes since MS2}

In MS2, we decomposed each dimension of our \texttt{Body}s into arrays, (e.g. the $x$ position, the $x$ veolocity, etc.), \texttt{MPI\_Scatterv}ed these arrays, recomposed them into \texttt{Body}s, ran \texttt{Leapfrog} on this subset on each node, decomposed the subset into arrays, \texttt{MPI\_Gatherv}ed these arrays back to the root node, and recomposed them into \texttt{Body}s. We were also allocating a fresh new \texttt{Vector} after \texttt{Body} recomposition. This was, frankly, insane, and took a program with very low memory usage and pressure in the serial implementation to one that constantly allocated and deallocated memory on every single step.

By declaring \texttt{MPI\_Datatype MPI\_Body} with \texttt{MPI\_Type\_contiguous(8, MPI\_DOUBLE, \&MPI\_Body)}, we're now able to send and receive subsets of \texttt{Body}s with just a single \texttt{MPI\_Scatterv} and \texttt{MPI\_Gatherv} call. We also \texttt{MPI\_Scatterv} and \texttt{MPI\_Gatherv} directly into \texttt{Vector}s allocated at the start of the program, without intermediate array allocations. This eliminated transient out-of-memory errors, and likely reduced MPI overhead.

Report content
   This content adds to the content from previous reports.  The ECP describes the previous reports as chapters, you can use this opportunity to do a cleanup edit of your previous content but you aren't required to do a major rewrite.
The content you will be adding should contain:
    The testing actually performed [Do not rewrite your previous section to match this]. Comment on any differences between your test plan and what you actually executed. Give your results.
    Analyse your results. Does your implementation scale? 
    Summarise your findings for the semester (eg what worked and what didn't) including any limitations you expect scaling up your implementation to solving truely massive problem instances.

Marking criteria: /20
  Code compiles out of repo /2
  Testing description       /8
  Analysis                  /6
  Summarise findings        /4
